### 2023-08-07 tesis_Luis/Chapter4/chapter4.tex
updated

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=.45\textwidth]{Chapter4/xscan.png}
\includegraphics[width=.45\textwidth]{Chapter4/yscan.png}\\
\caption[Fit for the vdM1 BCIDs 282 (x and y directions)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
\label{vdM1_282_XYscan}
\end{figure}
\end{center}
For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully. The evaluation of the goodness of fit is shown in Fig. \ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.

@@

The final result obtained is:
\begin{equation}
\sigma_{vis}=4163.3 \pm 3.3 \text{ (stat)  mb}
\end{equation}

@@

\begin{table}[h!]
\centering
\caption[Bunch-to-Bunch Uncertinties]{Systematic uncertainties corresponding to Bunch-to-Bunch variations.}
\label{bunch-to-bunch}
\begin{tabular}{lccc}
\multicolumn{1}{c}{\textbf{Scan}} & \textbf{$\sigma_{\textbf{vis}}$ (mb)} & \begin{tabular}[c]{@{}c@{}}\textbf{Standar}\\\textbf{Deviation~(STD) }\end{tabular} & \begin{tabular}[c]{@{}c@{}}\textbf{Syst. error}\\\textbf{$\text{STD/}(\sigma_{\textbf{vis}}*\sqrt{5})$}\end{tabular}  \\ 
\toprule
vdM1                              & 4147.71               & 12.56                                                                       & 0.13                                                                              \\
BI1                              & 4151.50               & 12.22                                                                       & 0.13                                                                              \\
BI2                              & 4146.04               & 5.39                                                                       & 0.05                                                                              \\
vdM3                              & 4174.31               & 9.18                                                                        & 0.10                                                                              \\
vdM4                              & 4145.64               & 6.96                                                                      & 0.08                                                                              \\ 
\hline
\textbf{Total}                    &                          &                                                                                & \textbf{0.1}                                                                    
\end{tabular}
\end{table}
%& \begin{tabular}[c]{@{}c@{}}\textbf{$STD/(\sigma_{vis}*\sqrt{5})}\\\textbf{[\%]}\end{tabular}  \\ 
\textbf{Background}: The value of the background systematic  is assigned as the  difference between the sigma visible value obtained with a DG+Constant Fit model (4163.3 mb) and our current DG fit model with background subtraction (4153.3 mb). This revealed a difference in the $\sigma_{vis}$ of 10.0 mb, corresponding to an assigned uncertainty of 0.24\%.\\

@@

\begin{table}[h!]
\centering
\caption[Systematic Uncertainties]{Total systematic uncertainties for the calibration.}
\label{systematics}
\begin{tabular}{lc}
                               & \multicolumn{1}{l}{}       \\
                               & \multicolumn{1}{l}{}       \\
            & \textbf{Systematic Uncertainty [\%]}  \\ 
\toprule
Length scale                   & 0.12                        \\
Orbit drift                    & 0.3                        \\
%Residual beam positions & 1.0                \\
%Factorization bias & 1.4                        \\
Beam-beam effects              & 0.5                        \\
Beam current calibration       & 0.2                        \\
Ghost and satellite            & 0.1                        \\
Scan to scan variation         & 0.26                        \\
Bunch to bunch variation       & 0.1                        \\
%Cross detector consistency     & -                          \\
Background subtraction         & 0.24                          \\ 
\hline
\textbf{Total}                 & \textbf{0.73}               
\end{tabular}
\end{table}

Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($77.8 \text{ mb}$). Therefore, the final value for $\sigma_{vis}$ is determined as:

\begin{equation}
\sigma_{vis} = 4153.3 \pm 2.7 \text{(stat.)} \pm 30.3 \text{(syst.) mb}
\end{equation}

>>>>

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=.45\textwidth]{Chapter4/xscan.png}
\includegraphics[width=.45\textwidth]{Chapter4/yscan.png}\\
\caption[Fit for the vdM1 BCIDs 282 (x and y directions)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
\label{vdM1_282_XYscan}
\end{figure}
\end{center}
For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully. The evaluation of the goodness of fit is shown in Fig. \ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.98.

@@

The final result obtained is:
\begin{equation}
\sigma_{vis}=4153.3 \pm 2.7 \text{ (stat)  mb}
\end{equation}

@@

\begin{table}[h!]
\centering
\caption[Bunch-to-Bunch Uncertinties]{Systematic uncertainties corresponding to Bunch-to-Bunch variations.}
\label{bunch-to-bunch}
\begin{tabular}{lccc}
\multicolumn{1}{c}{\textbf{Scan}} & \textbf{$\sigma_{\textbf{vis}}$ (mb)} & \begin{tabular}[c]{@{}c@{}}\textbf{Standar}\\\textbf{Deviation~(STD) }\end{tabular} & \begin{tabular}[c]{@{}c@{}}\textbf{Syst. error}\\\textbf{$\text{STD/}(\sigma_{\textbf{vis}}*\sqrt{5})$}\end{tabular}  \\ 
\toprule
vdM1                              & 4147.71               & 12.56                                                                       & 0.13                                                                              \\
BI1                              & 4151.50               & 12.22                                                                       & 0.13                                                                              \\
BI2                              & 4146.04               & 5.39                                                                       & 0.05                                                                              \\
vdM3                              & 4174.31               & 9.18                                                                        & 0.10                                                                              \\
vdM4                              & 4145.64               & 6.96                                                                      & 0.08                                                                              \\ 
\hline
\textbf{Average}                    &                          &                                                                                & \textbf{0.1}                                                                    
\end{tabular}
\end{table}
%& \begin{tabular}[c]{@{}c@{}}\textbf{$STD/(\sigma_{vis}*\sqrt{5})}\\\textbf{[\%]}\end{tabular}  \\ 
\textbf{Background}: The value of the background systematic  is assigned as the  difference between the sigma visible value obtained with a DG+Constant Fit model (4163.3 mb) and our current DG fit model with background subtraction (4153.3 mb). This revealed a difference in the $\sigma_{vis}$ of 10.0 mb, corresponding to an assigned uncertainty of 0.24\%.\\

@@

Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($30.3 \text{ mb}$).
\newpage
\begin{table}[!ht]
\centering
\caption[Systematic Uncertainties]{Total systematic uncertainties for the calibration.}
\label{systematics}
\begin{tabular}{lc}
                               & \multicolumn{1}{l}{}       \\
                               & \multicolumn{1}{l}{}       \\
            & \textbf{Systematic Uncertainty [\%]}  \\ 
\toprule
Length scale                   & 0.12                        \\
Orbit drift                    & 0.3                        \\
%Residual beam positions & 1.0                \\
%Factorization bias & 1.4                        \\
Beam-beam effects              & 0.5                        \\
Beam current calibration       & 0.2                        \\
Ghost and satellite            & 0.1                        \\
Scan to scan variation         & 0.26                        \\
Bunch to bunch variation       & 0.1                        \\
%Cross detector consistency     & -                          \\
Background subtraction         & 0.24                          \\ 
\hline
\textbf{Total}                 & \textbf{0.73}               
\end{tabular}
\end{table}

 %Therefore, the final value for $\sigma_{vis}$ is determined as:

%\begin{equation}
%\sigma_{vis} = 4153.3 \pm 2.7 \text{(stat.)} \pm 30.3 \text{(syst.) mb}
%\end{equation}
